%Preamble%
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%Packages%
%TikZ%
\usepackage{physics}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{mathdots}
\usepackage{yhmath}
\usepackage{cancel}
\usepackage{color}
\usepackage{siunitx}
\usepackage{array}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{booktabs}
\usetikzlibrary{fadings}
\usetikzlibrary{patterns}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes}
\usepackage{extarrows}
%Document Layout
\usepackage{geometry} %Page dimensions
\usepackage{fancyhdr} %Custom Headers
\usepackage{footmisc} %Custom Footers
\usepackage{titlesec} %Title and Section Formatting
\usepackage{array}
%Formatting Packages%
\usepackage{xcolor} %For color%
\usepackage{graphicx} %For Images%
%\graphicspath{ {images/} }
%Miscellaneous Packages%
%Bibliographies
\usepackage{hyperref} %Hyperlinks
\usepackage{enumitem} %Advanced Lists
\usepackage{comment} %Multiline Comments
%Math Packages%
\usepackage{mathtools, amsmath, nccmath, amsfonts, amssymb, amsthm, thmtools}
%Page Geometry%
\geometry{
    a4paper,
    total={170mm,257mm},
    left=20mm,
    top=20mm,
    headheight=14pt
}


%%%%%%%%%%%Dark Mode Stuff%%%%%%%%%%%%%%
%\definecolor{mybgcolor}{RGB}{6.9, 6.9, 6.9}
%\pagecolor{mybgcolor}
%\color[rgb]{1,1,1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Theorem Environments%
%Ref:https://math.ucsd.edu/~jeggers/latex/amsthdoc.pdf%
\theoremstyle{plain}% default 
\newtheorem{thm}{Theorem}[section] 
\newtheorem{lem}{Lemma}[thm] 
\newtheorem{prop}[lem]{Proposition} 
\newtheorem{cor}{Corollary}[thm]
\newtheorem*{claim}{Claim}
\newtheorem{case}{Case}
\theoremstyle{definition}
\newtheorem*{ques}{Question}
\newtheorem{conj}{Conjecture}[section]
\newtheorem{exmp}{Example}[section]
\newtheorem{exer}{Exercise}[section]
\theoremstyle{remark} 
\newtheorem*{note}{Note}

\newtheoremstyle{breakthm}% %For leaving a line after theorem header
	{}{}%
	{\itshape}{}%
	{\bfseries}{}%
	{\newline}{}
	% The above doesnt work really well with enum lists, so for that we have to start the theorem as 
	% \begin{breakthm}[...]
	% \leavevmode \vspace{-\baselineskip}
	% \begin{enumerate}
	%Use breakenum snippet for this!
	%For more info on thereom styles: Check this: http://www.ams.org/arc/tex/amscls/amsthdoc.pdf

\theoremstyle{breakthm}
\newtheorem{bthm}{Theorem}[section]
\newtheorem{blem}{Lemma}[section]

\newtheoremstyle{breakdefn}% %For leaving a line after defn header
	{}{}%
	{}{}%
	{\bfseries}{:}%
	{\newline}{}

\theoremstyle{breakdefn}
\newtheorem{defn}{Definition}[section] 
\newtheorem*{bques}{Question}
\newtheorem{bconj}{Conjecture}[section]
\newtheorem{bexmp}{Example}[section]
\newtheorem{bexer}{Exercise}[section]

\newtheoremstyle{breakrem}% %For leaving a line after remark header
	{}{}%
	{}{}%
	{\itshape \bfseries}{:}%
	{\newline}{}
	
\theoremstyle{breakrem}
\newtheorem*{rem}{Remark(s)}

%Command Changes%
\renewcommand{\contentsname}{Table of Contents:}
\renewenvironment{proof}{{\bfseries Proof.}}{ \\ \qed}

%New Custom Commands%
%Math Notations
\newcommand{\R}{{\mathbb R}}
\newcommand{\Z}{{\mathbb Z}}
\newcommand{\N}{{\mathbb N}}
\newcommand{\Q}{{\mathbb Q}}
\newcommand{\C}{{\mathbb C}}
\newcommand{\multdot}{\text{·}}
\newcommand{\sq}{\ensuremath{^2}}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
%Simple Footnote
\newcommand{\simplefn}[1]{\hfill \sl{\footnotesize{#1}} \\}
%Section Decoration
\newcommand{\sectiondecor}{
    \begin{center}
    \vspace{-0.2in}
    \line(1,0){300} \\
    \large{$\infty$}    
    \end{center}
}
%Syllabus Commands
\newcommand{\infopointer}[2]{\large{\textbf{#1:}} \textit{#2}}
%For Notes:
\newcommand{\remarklinebreak}{\hfill \break \vspace{-0.3in}}

%%%MAIN DOC BEGINS%%%
\title{Groups and Subgroups}
\author{\textbf{Sanjyot Shenoy}}
\date{2021}


\pagestyle{fancy}
\fancyhf{}
\lhead{Groups: Groups and Subgroups}
\rhead{Sanjyot Shenoy}
\rfoot{Page \thepage}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}
	\maketitle
	\tableofcontents
	\section{Introduction}
	\begin{defn}[Binary Operation]
		A binary operation $*$ on a set $G$ is a function $*:G\times G\to G$. We shall write $*(a,b)$ as $a*b$. 
	\end{defn}
	\begin{defn}[Associative Binary Operation]
		A binary operation $*$ on a set $G$ is said to be associative if $\forall a,b,c\in G$ we have that $a*(b*c)=(a*b)*c$.
	\end{defn}
	\begin{defn}[Commutative Binary Operation]
		A binary operation $*$ on a set $G$ is said to be commuative if $\forall a,b\in G$ we have $a*b=b*a$.
	\end{defn}
	\begin{bexmp}
		\leavevmode \vspace{-\baselineskip}
		\begin{enumerate}
			\item $+$ (usual addition) is a commutative binary operation on $\Z$ (or on $\Q$, $\R$, or $\C$ respectively). 
			\item $\times $ (usual multiplication) is a commutative binary operation on $\Z$ (or on $\Q$, $\R$, or $\C$ respectively).
			\item $-$ (usual subtraction) is a non-commutative binary operation on $\Z$, where $-(a,b)=a-b$. The map $a\mapsto -a$ is not a binary operation.
			\item Taking the  vector cross-product of two vectors in 3-space $\R^3$ is a binary operation which is not associative and not commutative.
		\end{enumerate}
	\end{bexmp}
	\begin{rem}
		\leavevmode \vspace{-\baselineskip}
		\begin{enumerate}
			\item  Suppose that $*$ is a binary operation on a set $G$ and $H\subset G$. If the restriction of $*$ to $H$ is a binary operation on $H$, i.e, $\forall a,b\in H$, $a*b\in H$, then  $H$ is said to be \textbf{closed} under $*$. 
			\item Observe that is $*$ is associative (respectively, commutative) binary operation on $G$ and $*$ restricted to some subset $H$ of $G$ is a binary operation on $H$, then $*$ is automatically associative (respectively, commutative) on $H$ as well. 
		\end{enumerate}
	\end{rem}
	\subsection{Group}
	\begin{defn}[Group]
		A \textbf{Group} is an ordered pair $(G,*)$ where $G$ is a set and $*$ is a binary operation on $G$ satisfying the following axioms:
		\begin{enumerate}
			\item (Associative) $(a*b)*c=a*(b*c)$, $\forall a,b,c\in G$, i.e.,$*$ is associative.
			\item (Existence of Identity) There exists an element $e$, called an identity of $G$, such that $\forall a\in G$, we have $a*e=e*a=a$.
			\item (Existence of Inverses) $\forall a\in G$, $\exists a^{-1}\in G$, called an inverse of $a$, such that $a*a^{-1}=a^{-1}*a=e$. 
		\end{enumerate}
	\end{defn}
	
	\begin{defn}[Abelian Group]
			A Group $(G,*)$ is said to be an Abelian group if the binary operation $*$ on $G$ is commutative for all elements of $G$.
	\end{defn}
	\begin{rem}
		\leavevmode \vspace{-\baselineskip}
		\begin{enumerate}
			\item We shall immediately become less formal and say G is a group under * if $(G,*)$ is a group (or just $G$ is a group when the operation $*$ is clear from the context).
			\item (Finite Group) - If the set $G$ is a finite set, then the group $G$ is called a finite group.
			\item (Non-emptiness of set): By axiom on existence of identity, the set $G$ is non-empty.
		\end{enumerate}
	\end{rem}
	\subsubsection*{Direct Product of Groups}
	If $(A,*)$ and $(B,\diamond )$ are groups, we can form a new group $A\times B$ called their \textbf{direct product}, whose elements are those in the Cartesian product.
	\[
		A\times B = \{(a,b)|a\in A,\, b\in B\}
	.\] 
	and whose operation is defined componentwise: 
	\[
		(a_{1},b_{1})(a_{2},b_{2}) = (a_{1}*a_{2},b_{1}\diamond b_{2})
	.\]
	It is easy to check that this is a group.


\end{document}
